%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}


\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Ronald H. Baker}{January 24, 1991 }{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:ronald_baker.at.brown.dot.edu}{ronald-baker\mbox{}@\mbox{}brown.edu}\sbull
\textsmaller401.xxx.xxxx\sbull

\href{https://www.linkedin.com/in/rhbaker2014/}{www.linkedin.com/in/rhbaker2014}
\\
99 SomeStreet Ave.\sbull
00000\thinspace {\large \sc}\sbull
Providence\sbull
Rhode Island

\spacedhrule{0.5em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{https://www.brown.edu/}{Brown University}}
  {\textsc{Providence, Rhode Island}} {%
  \headedsubsection
    {Master's of Science in Computer Science}
    {2016 -- present}
    {\bodytext{Focused on computer systems and robotic applications (\acr{RAD}) and the semantic web technology stack (\acr{RDF}/\acr{RDFS}, \acr{OWL} and \acr{SPARQL}).  Picked up quite some Java skills along the way.}}
}

\headedsection
  {\href{https://www.buffalo.edu/}{University at Buffalo: The State University of New York}}
  {\textsc{Buffalo, New York}} {%
  \headedsubsection
    {Bachelor's of Science in Electrical Engineering  \textnormal{\textit{~(first generation)}}}
    {2011 -- 2014} {\bodytext{Focused on computer systems and robotic applications (\acr{RAD}) and the semantic web technology stack (\acr{RDF}/\acr{RDFS}, \acr{OWL} and \acr{SPARQL}).  Picked up quite some Java skills along the way.}}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Software design and implementation, with(in) a team.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  { English \emph{(full professional proficiency)}.}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.hoppinger.com}{Hoppinger}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Head of Technology}
    {Apr \apo12 -- present}
    {\bodytext{Hoppinger is an open source minded ``full-service'' internet agency.  Reporting directly to the general director, Marijn Bom. In charge of drawing and carrying out the vision for the tech department consisting of 15 developers.  Streamlined datacenter operations with Puppet, introduced Rails for custom web-app development and Capistrano for deployment automation.  Intimately involved with the software architecture of all technically challenging projects.}}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {\href{http://www.hro.nl}{HRO} (Rotterdam University of Applied Science)}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Guest Lecturer}
    {Sep \apo12 -- present}
    {\bodytext{Introductory lecture on history of software development and open source for 1\textsuperscript{st} year CS students.}}
}

\headedsection
  {\href{http://www.intellecap.com}{Intellecap}/\href{http://istpl.in}{\acr{ISTPL}}}
  {\textsc{Mumbai, Pune \& Hyderabad, India}} {%

  \headedsubsection
    {\acr{IT} Consultant}
    {Nov \apo08 -- Feb \apo09}
    {\bodytext{Intellecap is a social-sector advisory firm serving corporates, non-profits, development agencies and governments working in developing markets. Assessed their software development team and methodologies, trained their developers and build several web applications.  One of those apps is \href{http://www.mostfit.org}{Mostfit}, an open source \acr{MIS} for \href{http://en.wikipedia.org/wiki/Microcredit}{microcredit} lenders.}}

  \headedsubsection
    {\acr{IT} \& Strategy Consultant}
    {Jan \apo10 -- Aug \apo11}
    {\bodytext{Called in to solve several technical challenges and look at potential growth strategies for \href{http://www.mostfit.org}{Mostfit}.}}

  \headedsubsection
    {CTO}
    {Oct \apo11 -- Feb \apo12}
    {\bodytext{Proudly joined the \acr{C}-family of Intellicap's software division, ISTPL, to make \href{http://www.mostfit.org}{Mostfit} the nr.1 software solution for micro credit lenders around the globe.  Contracts got terminated half a year later due to investment issues.}}
}

%\headedsection
%  {LIP Automatisering}
%  {\textsc{Breda, The Netherlands}} {%
%  \headedsubsection
%    {Software Auditor}
%    {Sep \apo06}
%    {\bodytext{Audited their flag ship product \emph{\acr{LIP} Suite}:\ an %\acr{ERP} solution for construction companies.}}
%}

\headedsection
  {\href{http://www.thehealthagency.com}{The Health Agency}}
  {\textsc{Delft \& Rotterdam, The Netherlands}} {%

  \headedsubsection
    {Software Engineer}
    {Jun \apo05 -- Feb \apo06}
    {\bodytext{Worked on their CMS (written in Python and uses Postgre\acr{SQL}, \acr{XML}/\acr{XSLT} and Twisted).}}

  \headedsubsection
    {Software Auditor}
    {Dec \apo06}
    {\bodytext{Assessed their Python/Zope/\acr{Z}o\acr{DB}-based web framework re-engineering project.}}
}

\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to my \href{http://www.linkedin.com/in/ciesbreijs}{Linked-in profile} for a more complete list of work experiences along with recommendations.}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {art, Buddhism, cryptography, Go (board game), history, music, open source, philosophy, software engineering (methodologies), travel, typography (e.g.\ graphic design, \LaTeX), \acr{UI}/\acr{UX}-design and vegetarian/vegan cooking.}


\end{document}

＀
